\fontfamily{phv}\selectfont{Research A Proposal}

### 2013-09-24 docs/proposal/doc.tex
Further work on motivation.

% Motivation
The brain and particularly the human brain have been studied for hundreds of years.
Today, the secrets of our brains still belong to the most sought-after secrets.
The techniques however have changed.
Today, advanced measurement methods exist that allow scientists to peek inside brains that give a coarse but broad overview without having to open a single skull.

Of particular interest are causal relations between brain regions and cognitive and bodily functions.
We have come a long way since the time of Phrenology, the pseudoscience based on the idea that cognitive ability and personality could be derived from measurements of the skull.
The question whether brain region X is somehow connected to brain region Y is still highly relevant; it is the main question of the present-day scientific field of brain connectivity.

Understanding brain structure implies understanding more about the brain as a whole.

Brain connectivity also finds applications in medicine.
Neuro-degenerative diseases such as Alzheimer's disease, Parkinson's disease, dementia, Amyotrophic lateral sclerosis (ALS) have all been shown to severely alter brain connectivity.
Better methods for analysing connectivity could lead to more insight in these diseases.

%This is part of why it is interesting to investigate neuro-degenerative disease, which are able to cripple our usually robust networks effectively.
%We want to learn more about our brains, as well as the diseases that target them.

Much progress has recently been made in the fields of structural and functional connectivity\cite{vandenheuvel2010}.
Research has also been done on inferring effective connectivity, based on Granger causality (Roebroeck, Formisano, Goebel, 2005), multivariate autoregressive modeling (Harrison, Penny, Friston, 2003) and dynamic causal modelling (Friston, Harrison, Penny, 2003).
However, many challenges are still being faced. (Ramsey, Hanson, Hanson, Halchenko, Poldrack , Glymour)

>>>>

% Motivation
The brain and particularly the human brain have been studied for hundreds of years.
Today, the secrets of our brains still are one of the most sought-after.
The techniques however have changed.
Today, advanced measurement methods exist that allow scientists to peek inside brains that give a coarse but broad overview without having to open a single skull.

Of particular interest are causal relations between brain regions and cognitive and bodily functions.
We have come a long way since the time of Phrenology, the pseudoscience based on the idea that cognitive ability and personality could be derived from measurements of the skull and, post-mortem, the brain.
The question whether brain region X is somehow connected to brain region Y is still highly relevant; it is the main question of the present-day scientific field of brain connectivity.
Understanding brain structure implies understanding more about the brain as a whole.

Not surprisingly, brain connectivity also finds applications in medicine.
Neuro-degenerative diseases such as Alzheimer's disease, Parkinson's disease, dementia, Amyotrophic lateral sclerosis (ALS) have all been shown to severely alter brain connectivity.
Better methods for analysing connectivity could lead to more insight in these diseases.

The field of brain connectivity finds its roots in the early 1990s \cite{friston1993functional, friston1994}, though because of more recent developments in the field of Artificial Intelligence and Machine Learning it is possible to do more thorough analysis \cite{vandenheuvel2010}.
One type of connectivity analysis involves in determining these causal relations between brain areas.
However, causal analysis still faces many challenges that require solutions \cite{ramsey2010}.
